---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SynopsisPackage

<!-- badges: start -->
<!-- badges: end -->

The goal of `SynopsisPackage` is to identify the data format and import the dataset if the correct data format is provided. After successfully importing the dataset, the package will provide a comprehensive summary that includes the following metadata:

- **Class**: The class of the dataset.
- **Data Type**: The type of the dataset.
- **Dimensions**: The dimensions of the dataset (rows and columns).
- **Structure**: The structure of the dataset.
- **Column Names**: The names of the columns in the dataset.
- **Missing Values**: Detailed information about missing values in the dataset.
- **Imported Dataset**: The dataset itself, loaded into your environment.

By using this package, users can easily identify, read, and understand the basic structure and characteristics of their data.

## Installation

```{r dependencies}
# install.packages("usethis")
# install.packages("devtools")
# install.packages("readxl)
# install.packages("tools)
# install.packages("tidyverse)
```


You can install the development version of SynopsisPackage from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("NareshdeBruijn14/SynopsisPackage")
library(synopsis)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# library(SynopsisPackage)
# 
# synopsis("./data/species.csv")
# 
# results <- synopsis("./data/species.csv")
# 
# print(results$data) # will give you the whole imported dataset
# print(results$class) # gives you what kind of class the dataset is
# print(results$dim) # gives the dimentions of the dataset
# print(results$str) # gives the list structure of the dataset
# print(results$typeof) # gives the data type(s) 
# print(results$names) # gives the header names of the dataset (if present)
# print(results$NA_info) # gives a list of information about the missing values in the dataset(if present)

```


